On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-01 docs/mvfits_paper/mvf.tex
Rephrase polynomial ansatz inapplicability [24]

\par Despite the apparent universality of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a low order multinomial.

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order.

>>>>

\par Despite the apparent universality of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a polynomial.

@@

Worst, in cases where the underlying dataset is best described by a rational function, a rational model with maximum monomial degree $K$ will typically outperform a polynomial model of maximum degree $K$ with the same number of coefficients as the rational model.
